\section{Precursor emissions' contributions to methane radiative forcing in RCP 6.0}

Previous work has calculated global values of the sensitivity of methane lifetimes to precursor emissions~\citep{ref:fry2012,ref:holmes2013}. The spatially explicit sensitivity values (shown in Figure~\ref{fig:rfsens} in Methods) calculated with the adjoint model aggregate into a normalized global annual mean sensitivity of the methane lifetime with respect to tropospheric OH to land-based anthropogenic NOx, CO, and NMHC emissions (i.e., $d \mathrm{ln}(\tau)/d\mathrm{ln}(\mathrm{E})$) of -0.15, 0.07, and 0.03 respectively, comparable to results adopted by~\citet{ref:holmes2013} of -0.14 $\pm$ 0.03, 0.06 $\pm$ 0.02, and 0.04 $\pm$ 0.01. If the aggregated value is used, a doubling of land-based anthropogenic NOx emissions would lead to a methane lifetime reduction of $\approx$ 10\%, approximately a factor of 2 higher than a similar combined change in CO and NMHC emissions, which act in the opposite direction. However, if the spatially explicit sensitivity values are taken into account, the doubling of land-based anthropogenic NOx emissions leads to a reduction of $\approx$ 15\% in the methane lifetime because some of the regions with larger emissions also have larger than average sensitivity.

%However, the method employed here enables the study of regional differences in how methane radiative forcing responds to changes in precursor emissions, and what that implies for the climate impacts of future air quality control and climate change mitigation strategies. As an example, we calculate the methane radiative forcing due to emissions changes projected under representative concentration pathway (RCP) 6.0~\citep{ref:vanvuuren2011}.

The projected change in methane RF can be spatially attributed to NOx, CO, NMHC, and CH4 emissions according to RCP 6.0 between 2000 and 2050 as shown in Figure~\ref{fig:eqems}. RCP 6.0, a medium scenario in terms of mitigation efforts, projects roughly a 20\% (or 25 Tg/yr) decrease in global NOx emissions from 2000 levels by 2050, and up to a 60\% decrease at 2100. CO and NMHC emissions are projected to change by 3\% (37 Tg/yr) and 4\% (9 Tg/yr) between 2000-2050. Methane emissions globally increase by 18\% (55 Tg/yr) by 2050, but then decrease by a similar margin below the 2000 baseline by 2100. Tropical and subtropical regional changes in emissions are amplified by enhanced sensitivity from high surface temperatures, which increase OH production (see Figure~\ref{fig:rfsens} in Methods). We also weigh the relative importance of emissions that alter the chemical sink term with the projected direct source emissions of methane itself. The balance of these two terms (shown in the bottom right of Figure~\ref{fig:eqems}) is projected to be a mix of positive and negative forcings that depends on the local change in each species as well as the sensitivity of the methane loss rate to emissions of said species. In particular, Chinese emissions dominate both positive and negative RF from CO+NMHC and NOx emissions, respectively, while playing significant role in direct methane reductions.  The net methane RF is a sensitive balance between these competing terms leading to a complex spatial pattern in the sensitivity of RF to emissions, which will be discussed in more detail in Section~\ref{sec:china}.  Similarly, projected increases in direct CH4 RF throughout India are offset by negative RF from increased NOx emissions leading an overall negative RF in the southern India, while an overall positive RF remains in the Indo-Gangetic plain.  

