\section{Results}

Figure~\ref{fig:rfsens} shows the sensitivity of global methane radiative forcing in July to various precursor emissions. The negative sign for NOx sensitivity implies that increases in NOx emissions lower the global methane radiative forcing, because higher emissions locally decrease hydroxyl radical concentrations, reducing the loss of methane, while the inverse is true for CO emissions. The sensitivities are generally largest at low latitudes where hydroxyl radical concentrations are highest. Certain locations provide more favorable access to the global atmosphere through high altitude (e.g. Mexico City) or strong convection (e.g. southeastern Asia), giving emissions in those locations a stronger influence on the global mean methane loss rate~\citep{ref:bowman2012}.

High sensitivities in general do not map to the locations of largest emissions for NOx, but for CO and some of the longer-lived VOCs the highest sensitivities do occur in strong source regions. Why would this be?

Sensitivities with respect to anthropogenic NOx are greater than those with respect to CO or VOCs. However, methane loss rates are also highly sensitive to lightning NOx emissions and these can be locally dominant, for instance in central Africa.

Methane radiative forcing is about ten times more sensitive to changes in anthropogenic NOx than to anthropogenic VOCs (here, the combination of ALK4, ALD2, MEK, PRPE, C3H8, C2H6, and CH2O). This is partly because some VOCs (CH2O in particular) can contribute a negative forcing in certain chemical environments which offsets the general increase of OH with increasing VOC emissions. The VOC sensitivity can be comparable to NOx in some polluted regions, for instance the Ganges valley.

% Need to find a metric to compare overall 'strength' of sensitivity